### 2018-02-14 Writing/Thesis/content/chapter-appendix.tex
more writing
more table and figure overhaul

% !TEX root = ../my-thesis.tex
%
\chapter{Example Appendix}
\label{sec:appendix}

\section{Appendix Section 1}
\label{sec:appendix:sec1}

\begin{table}[h]
	\begin{tabularx}{\textwidth}{X | X | X}
		%\hline
		Alpha		& Beta			& Gamma			\\ \hline
		0			& 1				& 2				\\ \hline
		3			& 4				& 5				\\ %\hline
	\end{tabularx}
	\label{tab:table1}
	\caption{This is a caption text.}
\end{table}

>>>>

% !TEX root = ../my-thesis.tex
%
\chapter{Appendix}
\label{sec:appendix}

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X}
	\multicolumn{1}{>{\centering\arraybackslash}X}{Meta Feature Group} \\
	\hline \hline
	\multicolumn{1}{>{\centering\arraybackslash}X}{NominalAttDistinctValues} \\ \hline
	MaxNominalAttDistinctValues, MinNominalAttDistinctValues, MeanNominalAttDistinctValues, StdvNominalAttDistinctValues \\ \hline
	\multicolumn{1}{>{\centering\arraybackslash}X}{SimpleMetaFeatures} \\ \hline
	NumberOfInstances, NumberOfFeatures, NumberOfClasses, Dimensionality, NumberOfInstancesWithMissingValues, NumberOfMissingValues, PercentageOfInstancesWithMissingValues, PercentageOfMissingValues, NumberOfNumericFeatures, NumberOfSymbolicFeatures, NumberOfBinaryFeatures, PercentageOfNumericFeatures, PercentageOfSymbolicFeatures, PercentageOfBinaryFeatures, MajorityClassSize, MinorityClassSize, MajorityClassPercentage, MinorityClassPercentage, AutoCorrelation \\ \hline
	\multicolumn{1}{>{\centering\arraybackslash}X}{Cardinality} \\ \hline
	MeanCardinalityOfNumericAttributes, StdevCardinalityOfNumericAttributes, MinCardinalityOfNumericAttributes, MaxCardinalityOfNumericAttributes, MeanCardinalityOfNominalAttributes, StdevCardinalityOfNominalAttributes, MinCardinalityOfNominalAttributes, MaxCardinalityOfNominalAttributes, CardinalityAtTwo, CardinalityAtThree, CardinalityAtFour \\ \hline
	\multicolumn{1}{>{\centering\arraybackslash}X}{Statistical} \\ \hline
	MeanMeansOfNumericAtts, MeanStdDevOfNumericAtts, MeanKurtosisOfNumericAtts, MeanSkewnessOfNumericAtts, MinMeansOfNumericAtts, MinStdDevOfNumericAtts, MinKurtosisOfNumericAtts, MinSkewnessOfNumericAtts, MaxMeansOfNumericAtts, MaxStdDevOfNumericAtts, MaxKurtosisOfNumericAtts, MaxSkewnessOfNumericAtts, Quartile1MeansOfNumericAtts, Quartile1StdDevOfNumericAtts, Quartile1KurtosisOfNumericAtts, Quartile1SkewnessOfNumericAtts, Quartile2MeansOfNumericAtts, Quartile2StdDevOfNumericAtts, Quartile2KurtosisOfNumericAtts, Quartile2SkewnessOfNumericAtts, Quartile3MeansOfNumericAtts, Quartile3StdDevOfNumericAtts, Quartile3KurtosisOfNumericAtts, Quartile3SkewnessOfNumericAtts \\ \hline
	\multicolumn{1}{>{\centering\arraybackslash}X}{Landmarkers\footnotemark{}} \\ \hline
	DecisionStump, RandomTreeDepth1, RandomTreeDepth2, RandomTreeDepth3, REPTreeDepth1, REPTreeDepth2, REPTreeDepth3, J48.001., J48.0001., J48.00001., NaiveBayes, kNN1N, CfsSubsetEval kNN1N, CfsSubsetEval NaiveBayes, CfsSubsetEval DecisionStump \\ 
	\end{tabularx}
	\label{tab:metaFeatureDetails}
	\caption{The meta features computed by each meta feature group. More details can be found on \href{www.openml.org}{www.openml.org}.}
\end{table}

\footnotetext{Each landmarker represents its own group of meta features consisting of AUC, ErrRate and Kappa. All are computed with 2-fold crossvalidation.}

### 2018-02-14 Writing/Thesis/content/chapter-approach.tex
more table and figure overhaul

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:performanceValues}
	\caption{This is a caption text.}
\end{table}

@@

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
...
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\label{tab:regressionTables}
	\caption{This is a caption text.}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/regression_models.pdf}
\caption{A model of the regression based ranker}
\label{fig:regression_ranker_model}
\end{figure}

@@

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\
		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\
		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:preferenceTable}
	\caption{This is a ranking}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
\caption{A model of the preference based ranker}
\label{fig:preference_ranker_model}
\end{figure}

>>>>

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1			& MF 2		& ... 	& MF n		& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$		& $v_{12}$	& ...	& $v_{1n}$	& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$		& $v_{22}$	& ...	& $v_{2n}$	& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\ 
		...			& ...		& ...	& ...		& ...		& ...		&	...	&	...			\\ 
		$v_{m1}$		& $v_{m2}$	& ... 	& $v_{mn}$	& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:performanceValues}
	\caption{Training data for the rankers.}
\end{table}

@@

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 1	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{11}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{21}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m1}$				\\ \hline\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value 2 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{12}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{22}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{m2}$					 
	\end{tabularx}
}	
\vspace{1em}
...
\vspace{1em}	
\resizebox{\textwidth}{!}{%
	\begin{tabularx}{1.1\textwidth}{X | X | X | X}
		%\hline
		Meta Feature 1	& ... 	& Meta Feature n		& Performance Value k 	\\ \hline
		$v_{11}$			& ...	& $v_{1n}$			& $p_{1k}$				\\ 
		$v_{21}$			& ...	& $v_{2n}$			& $p_{2k}$				\\ 
		...				& ...	& ...				& ...					\\ 
		$v_{m1}$			& ... 	& $v_{mn}$			& $p_{mk}$					 
	\end{tabularx}
}
	\label{tab:regressionTables}
	\caption{How the regression ranker processes the training data.}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/regression_models.pdf}
\caption{An overview of how a regression based ranker constructs a ranking.}
\label{fig:regression_ranker_model}
\end{figure}

@@

\begin{table}[h]
\centering
	\begin{tabularx}{\textwidth}{X | X | X | X | X | X | X | X}
		%\hline
		MF 1				& MF 2				& ... 	& MF n				& PV 1 		& PV 2 		&	...	&	PV k 		\\ \hline
		$v_{11}$			& $v_{12}$			& ...	& $v_{1n}$			& $p_{11}$	& $p_{12}$	& 	...	&	$p_{1k}$		\\ 
		$v_{21}$			& $v_{22}$			& ...	& $v_{2n}$			& $p_{21}$	& $p_{22}$	& 	...	&	$p_{2k}$		\\
		...				& ...				& ...	& ...				& ...		& ...		&	...	&	...			\\
		$v_{m1}$			& $v_{m2}$			& ... 	& $v_{mn}$			& $p_{2m}$	& $p_{m2}$	& 	...	&	$p_{mk}$			 
	\end{tabularx}
	\label{tab:preferenceTable}
	\caption{How the preference ranker processes the training data.}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=1]{gfx/label_ranking_model.pdf}
\caption{An overview of how a preference based ranker constructs a ranking.}
\label{fig:preference_ranker_model}
\end{figure}

### 2018-02-14 Writing/Thesis/content/chapter-fundamentals.tex
more table and figure overhaul

Suppose an aspiring gardener wants to learn how to distinguish between different species of iris plants, a genus of ornamental plants with colorful flowers. More specifically, the focus lies on the three species iris versicolor, virginica and setosa. In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species, which is illustrated in Table \ref{tab:iris}. The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered three) an unknown iris plant is. The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation. They observe that all iris setosa plants from his sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species. The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants. While this model (illustrated in Fig. \ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | X}
		%\hline
		\multicolumn{1}{X}{Sepal length}	& \multicolumn{1}{X}{Sepal width}	& \multicolumn{1}{X}{Petal length}	& \multicolumn{1}{X}{Petal width} & Species			\\ \hline
				5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\caption{The information the gardener in the example could have gathered; this is an excerpt from the well known iris data set \cite{iris}}
	\label{tab:iris}
\end{table}

%\tikzsetnextfilename{DecisionTree}
\begin{figure}
\includegraphics[width=\textwidth]{gfx/placeholder_decisionTree}
\caption{PLACEHOLDER: The decision tree constructed as a simple model in the gardening example to classify iris species}
\label{fig:decision_tree}
\end{figure}

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. They then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.

\begin{figure}
\includegraphics[width=\textwidth]{gfx/placeholder_learning}
\caption{PLACEHOLDER: The learning problem, adapted from \cite{abu2012learning}}
\label{fig:learning_problem}
\end{figure}

@@

\begin{table}[h]
\centering
	\begin{tabularx}{.8\textwidth}{>{\hsize=0.9\hsize}X | >{\hsize=.1\hsize}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash} >{\hsize=.1\hsize}X}
		%\hline
		Species		& 	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris virginica}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris versicolor}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris setosa}	& 	\\ \hline
		Label		& [ & 1,									& 2,										& 3 									& ] \\ 
		Score		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
		Ranking		& [ & 2,									& 3,										& 1 									& ] \\ 
		Ordering		& [ & 3,									& 1,										& 2 									& ] \\ 		
	\end{tabularx}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
	\label{tab:ranking_vs_ordering}
\end{table}

>>>>

Suppose an aspiring gardener wants to learn how to distinguish between different species of iris plants, a genus of ornamental plants with colorful flowers. More specifically, the focus lies on the three species iris versicolor, virginica and setosa. In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species, which is illustrated in Table \ref{tab:iris}. The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered three) an unknown iris plant is. The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation. They observe that all iris setosa plants from his sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species. The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants. While this model (illustrated in Figure \ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | >{\raggedleft\arraybackslash}X | X}
		%\hline
		\multicolumn{1}{X}{Sepal length}	& \multicolumn{1}{X}{Sepal width}	& \multicolumn{1}{X}{Petal length}	& \multicolumn{1}{X}{Petal width} & Species			\\ \hline
				5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\caption{Features of different iris plants. This is an excerpt from the well known iris data set \cite{iris}}
	\label{tab:iris}
\end{table}

%\tikzsetnextfilename{DecisionTree}
\begin{figure}
\centering
\includegraphics[scale=.75]{gfx/decision_tree.pdf}
\caption{The decision tree constructed as a simple model  to classify iris plants in the gardening example.}
\label{fig:decision_tree}
\end{figure}

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. They then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$. An overview of this learning problem is provided in Figure \ref{fig:learning_problem}.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{gfx/machine_learning.pdf}
\caption{The learning problem, adapted from \cite{abu2012learning}.}
\label{fig:learning_problem}
\end{figure}

@@

\begin{table}[h]
\centering
	\begin{tabularx}{.8\textwidth}{>{\hsize=0.9\hsize}X | >{\hsize=.1\hsize}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\hsize=1.6\hsize\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash} >{\hsize=.1\hsize}X}
		%\hline
		Species		& 	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris virginica}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris versicolor}	& \multicolumn{1}{>{\hsize=1.6\hsize\centering\arraybackslash}X}{iris setosa}	& 	\\ \hline
		Label		& [ & 1,									& 2,										& 3 									& ] \\ 
		Score		& [ & 0.17,								& 0.12,									& 0.89 								& ] \\ 
		Ranking		& [ & 2,									& 3,										& 1 									& ] \\ 
		Ordering		& [ & 3,									& 1,										& 2 									& ] \\ 		
	\end{tabularx}
	\caption{Ranking and ordering in direct comparison.}
	\label{tab:ranking_vs_ordering}
\end{table}
